\chapter{Methodology}
This section includes a write up on tools and methods used while implementation. It lays down a clear description of the process used during development and testing.
\section{Tools}
There are variety of tools used during development of project. Major tools used have been listed below:
\begin{itemize}
    \item \textbf{Face verification system:}
    \begin{itemize}
        \item \textbf{Pytorch:} It is an open-source machine learning library based on the Torch library, used for computer vision and natural language processing applications, primarily developed by Facebook's AI Research lab. It is free and open-source software released under the Modified BSD license.
        \item \textbf{Other libraries:} Numpy, matplotlib, MXNet, Scipy, OpenCV, PIL, Scikit.
    \end{itemize}
    \item \textbf{Web interface:}
    \begin{itemize}
        \item \textbf{React.JS:} React is a free and open-source front-end JavaScript library for building user interfaces or UI components.
        \item \textbf{Express.JS:} Express is a minimal and flexible Node.js web application framework that provides a robust set of features for web applications.
        \item \textbf{Node.JS:} Node.js is an open-source, cross-platform, back-end JavaScript runtime environment that runs on the V8 engine and executes JavaScript code outside a web browser.
        \item \textbf{MongoDB:} MongoDB is a source-available cross-platform document-oriented database program. Classified as a NoSQL database program, MongoDB uses JSON-like documents with optional schemas.
    \end{itemize}
\end{itemize}
\section{Workflow}
The workflow followed during the implementation is as follows:\\
\textbf{Step 1:} Data collection for Machine learning model\\
\textbf{Step 2:} Prepare an augmentation pipeline\\
\textbf{Step 3:} Train model using ArcFace loss function without modifications\\
\textbf{Step 4:} Record results\\
\textbf{Step 5:} Train model with modified loss function\\
\textbf{Step 6:} Record results\\
\textbf{Step 7:} Build API for system using Node.JS, Express.JS, Twilio API, Stripe API\\
\textbf{Step 8:} Test and document API using Postman\\
\textbf{Step 9:} Build UI for web application using React.JS\\
\textbf{Step 10:} Integrate Frontend and Backend\\
\textbf{Step 11:} Test, and document the final system.

\section{Conclusion}
This section presented the workflow followed during the implementation of the system. We used Agile system of software engineering to complete the system in pre-decided timeline.